---
title: "DATA621_Homework4"
author: "Jenny"
date: "November 30, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

install.packages("DataExplorer")
install.packages("corrplot")
install.packages("leaps")
install.packages("mlogit")
install.packages("lattice")

```{r }

library(ggplot2)
library(stringr)
library(reshape2)
```

# Introduction
### In this homework, I will explore, analyze and model a data set containing approximately 8000 records representing a customer at an auto insurance company.Each record has two response variables. The first response variable, TARGET_FLAG, is a 1 or a 0. A "1" means that the person was in a car crash. A zero means taht the person was not in a car crash. The second response variable is TARGET_AMT. This value is zero if the person did not crash their car. But if they did crash their car, this number will be a value greater than zero. 
### My objective is to build multiple linear regression and binary logistic regression models on the training data to predict the probability 
# that a person will crash their car and also the amount of money it will cost if the person does crash their car. 


### Read the data set


```{r }
train_data <- read.csv("https://raw.githubusercontent.com/JennierJ/DATA621/master/Homework4/insurance_training_data.csv")
eval_data <- read.csv("https://raw.githubusercontent.com/JennierJ/DATA621/master/Homework4/insurance-evaluation-data.csv")
```

## Data Exploration and Cleaning
```{r }
head(train_data)
summary(train_data)
train_data <- train_data[,-1]
eval_data <- eval_data[,-1]
```
### Remove the unwanted characters from the data set fields.
```{r }
for(column in c("INCOME","HOME_VAL","BLUEBOOK","OLDCLAIM"))
{
  train_data[,column] <- str_replace_all(train_data[,column],pattern='\\$',replace='')
  train_data[,column] <- str_replace_all(train_data[,column],pattern=',',replace='')
  train_data[,column] <- as.numeric(as.vector(train_data[,column]))
}

train_data[sapply(train_data, is.factor)] <- lapply(train_data[sapply(train_data, is.factor)], 
                                        function(x) str_replace(x,"z_|<",""))

for(column in c("INCOME","HOME_VAL","BLUEBOOK","OLDCLAIM"))
{
  eval_data[,column] <- str_replace_all(eval_data[,column],pattern='\\$',replace='')
  eval_data[,column] <- str_replace_all(eval_data[,column],pattern=',',replace='')
  eval_data[,column] <- as.numeric(as.vector(eval_data[,column]))
}

eval_data[sapply(eval_data, is.factor)] <- lapply(eval_data[sapply(eval_data, is.factor)], 
                                                    function(x) str_replace(x,"z_|<",""))
```

## Data Preparation 
```{r }
summary(train_data)
nrow(train_data)
# Replacing N/A with mean for calculation
train_data$AGE[is.na(train_data$AGE)] <- mean(train_data$AGE, na.rm=TRUE)
train_data$YOJ[is.na(train_data$YOJ)] <- mean(train_data$YOJ, na.rm=TRUE)
train_data$INCOME[is.na(train_data$INCOME)] <- mean(train_data$INCOME, na.rm=TRUE)
train_data$HOME_VAL[is.na(train_data$HOME_VAL)] <- mean(train_data$HOME_VAL, na.rm=TRUE)
train_data$CAR_AGE[is.na(train_data$CAR_AGE)] <- mean(train_data$CAR_AGE, na.rm=TRUE)

```


##  Histograms
```{r }
ggplot(melt(train_data), aes(x=value)) + facet_wrap(~variable, scale="free") + geom_histogram(bins=50)
```

##  Boxplot
```{r }
ggplot(melt(train_data), aes(x=factor(variable), y=value)) + facet_wrap(~variable, scale="free") + geom_boxplot()
```


## Build Model
```{r }
# Logistic Regression with all variables
glm.fit = glm(TARGET_FLAG ~ . - TARGET_AMT, data = train_data,
              family = binomial)
summary(glm.fit)
# Exclude the predictor that are not significant
glm.fit1 = glm(TARGET_FLAG ~ KIDSDRIV + INCOME + PARENT1 + HOME_VAL
               + MSTATUS + JOB, data = train_data,
               family = binomial)
summary(glm.fit1)
```

## Using selected model to predict evaluation dataset 
```{r }
glm.probs.pred = predict(glm.fit1, newdata = eval_data, type = "response")
predtarget <- ifelse(glm.probs.pred > 0.5, 1, 0)
eval_data$pred <- predtarget
eval_data
table(predtarget)
summary(glm.probs.pred)
```

